NMRlipids IV: Headgroup \& glycerol backbone structures, and cation binding in bilayers with PE and PG lipids

### 2020-09-01 Manuscript/manuscriptPGPE.tex
Update P-N vector angle and order parameters results to the manuscript
Update dihedral and ion binding results in the manuscript

      POPC:POPG (1:1)/K$^+$  & CHARMM36 \cite{??}        &0          & 0  & 250:250 & 18158 & 0   &  298  & 200 & 200 & \cite{CHARMM36POPCPOPG5050} \\ 

@@

      POPC:POPG (1:1)        & CHARMM36 \cite{??}        &0          & 1.36  \todoi{Concentration calculated based in total amount of calcium ions. This may not be reasonable due to the lack of counterions.} & 250:250 & 18114 & 445  &  298  & 200 & 200 & \cite{CHARMM36POPCPOPG50501000mMCaCl} \\
      POPC:POPG (4:1)/K$^+$  & CHARMM36 \cite{??}        &0          & 0  & 400:100 & 18664 & 0  &  298  & 200 & 200 & \cite{CHARMM36POPCPOPG4010} \\
      POPC:POPG (4:1)/K$^+$  & CHARMM36 \cite{??}        &0          & 1.0 \todoi{Concentration calculated based in total amount of calcium ions. This may not be reasonable due to the lack of counterions.} & 400:100 & 18647 & 419  &  298  & 200 & 200 & \cite{CHARMM36POPCPOPG40101000mMCaCl} \\

@@

\begin{figure*}[!h]
  \centering
  \includegraphics[width=18.0cm]{../Figs/PCPEPGPSstructures.png}
  \includegraphics[width=8.0cm]{../Figs/CHARMMfromLIPIDS.eps}
  \includegraphics[width=8.0cm]{../Figs/PCPEPGPSdihedrals1.png}
  \includegraphics[width=8.0cm]{../Figs/PCPEPGPSdihedrals2.png}
  \includegraphics[width=8.0cm]{../Figs/HGtilt.png}
  \caption{\label{structures}
    Overlayed snapshots and dihedral angle distributions from CHARMM36 simulations of different lipids
    which give the best agreement with experiments.
  }
  \todo{The differences observed in dihedral distributions are not visible in the snapshot figures.} \\
  \todo{Why integral of the P-N angle distributions are not the same?} \\
  \todo{More detailed discussion of this figure is in https://github.com/NMRLipids/NMRlipidsIVPEandPG/issues/9} \\
\end{figure*}

@@

\clearpage
\subsection{Calcium binding to PE and PG lipid bilayers}
\begin{figure*}[bt]
  \centering
  \includegraphics[width=18.0cm]{../Figs/CHANGESwithCaClPG1PC1.eps}
  \caption{\label{changesWITHCaClPG}
    Modulation of headgroup order parameters of POPC ({\it left}) and POPG ({\it right}) in POPC:POPG (1:1)
    mixture upon addition of CaCl$_2$ in 298 K temperature from experiments \cite{borle85,macdonald87} and simulations.
    The $\beta$-carbon order parameter of POPC (dashed line on top left) is not directly measured but
    calculated from empirical relation $\Delta S_{\beta}=0.43\Delta S_{\alpha}$ \cite{akutsu81}.
    The changes with respect to the systems without CaCl$_2$ are shown for other data than
    for the $\alpha$-carbon of POPG for which experimental order parameter is not available.
    %(right) The headgroup order parameters of PG from PC:PG mixtures as a function CaCl$_2$
    %concentration from experiments \cite{borle85} and CHARMM36 simulations.
  }
    \todo{CHARMM36 simulations should be longer and with Na couterions.}
\end{figure*}

@@

\begin{figure}[]
  \centering
  \includegraphics[width=8.0cm]{../Figs/CAdensPG1PC1.eps}
  \caption{\label{CAdensPG}
    Calcium ion density profiles along membrane normal from simulations of POPC:POPG (1:1) mixtures with different force fields.
  }
\end{figure}

>>>>

      POPC:POPG (1:1)        & CHARMM36 \cite{??}        &0          & 0  & 150:150 & 31500 & 0   &  298  & 500 & 400 & \cite{CHARMM36POPCPOPG5050} \\ 

@@

      POPC:POPG (1:1)        & CHARMM36 \cite{??}        &0          & 1.08 & 150:150 & 29766 & 578  &  298  & 500 & 400 & \cite{CHARMM36POPCPOPG50501000mMCaCl} \\
      POPC:POPG (4:1)        & CHARMM36 \cite{??}        &0          & 0  & 350:88 & 26280 & 0  &  298  & 500 & 400 & \cite{CHARMM36POPCPOPG4010} \\
      POPC:POPG (4:1)        & CHARMM36 \cite{??}        &0          & 0.1 & 350:88 & 26280 & 47  &  298  & 500 & 400 & \cite{CHARMM36POPCPOPG4010100mMCaCl} \\
      POPC:POPG (4:1)        & CHARMM36 \cite{??}        &0          & 1.0 & 350:88 & 24927 & 451  &  298  & 500 & 400 & \cite{CHARMM36POPCPOPG40101000mMCaCl} \\

@@

\begin{figure*}[!h]
  \centering
  \includegraphics[width=18.0cm]{../Figs/PCPEPGPSstructures.png}
  \includegraphics[width=8.0cm]{../Figs/CHARMMfromLIPIDS.eps}
%  \includegraphics[width=8.0cm]{../Figs/PCPEPGPSdihedrals1.png}
%  \includegraphics[width=8.0cm]{../Figs/PCPEPGPSdihedrals2.png}
  \includegraphics[width=8.0cm]{../Figs/PNangleNORM.eps}
  \includegraphics[width=8.0cm]{../Figs/DIHEDRALS.eps}
  \caption{\label{structures}
    Overlayed snapshots and dihedral angle distributions from CHARMM36 simulations of different lipids
    which give the best agreement with experiments.
  }
  \todo{The differences observed in dihedral distributions are not visible in the snapshot figures.} \\
  \todo{More detailed discussion of this figure is in https://github.com/NMRLipids/NMRlipidsIVPEandPG/issues/9} \\
\end{figure*}

@@

\clearpage
\subsection{Calcium binding to PE and PG lipid bilayers}
\begin{figure*}[bt]
  \centering
  \includegraphics[width=18.0cm]{../Figs/CHANGESwithCaClPG1PC1.eps}
  \caption{\label{changesWITHCaClPG}
    Modulation of headgroup order parameters of POPC ({\it left}) and POPG ({\it right}) in POPC:POPG (1:1)
    mixture upon addition of CaCl$_2$ in 298 K temperature from experiments \cite{borle85,macdonald87} and simulations.
    The $\beta$-carbon order parameter of POPC (dashed line on top left) is not directly measured but
    calculated from empirical relation $\Delta S_{\beta}=0.43\Delta S_{\alpha}$ \cite{akutsu81}.
    The changes with respect to the systems without CaCl$_2$ are shown for other data than
    for the $\alpha$-carbon of POPG for which experimental order parameter is not available.
    %(right) The headgroup order parameters of PG from PC:PG mixtures as a function CaCl$_2$
    %concentration from experiments \cite{borle85} and CHARMM36 simulations.
  }
  \todo{Data for CHARMM with 100mM is still coming.}
\end{figure*}

@@

\begin{figure}[]
  \centering
  \includegraphics[width=8.0cm]{../Figs/CAdensPG1PC1.eps}
  \caption{\label{CAdensPG}
    Calcium ion density profiles along membrane normal from simulations of POPC:POPG (1:1) mixtures with different force fields.
  }
  \todo{Density of CHARMM simulation still to be updated from the new data.}
\end{figure}
